---
title: "Test speed-up and scale-up of R-Rerf against xg and ranger"
author: "James Browne"
date: "Oct 10 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = FALSE)
##source('rfr_function.R')
library(ggplot2)
nTimes <- 10
run_su <- TRUE
leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))


```{r speed_up_printRerf, cache = FALSE}
if(TRUE){
load(file="exp0037.Rdata")
load(file="exp0037Anum.Rdata")
lab <- labs(title="Forest Algorithm Strong Scaling", x="Number of Cores", y="Relative Performance", subtitle =paste("Dataset Size: p53(31159x5409)"))
print(ggplot(ress1,aes(x=Cores_Used, y=Speed_Up, group=Line_Type, color=Line_Type))+geom_line()+lab +leg+geom_text(x = 15, y =40 , label =paste("Amdahl Number\nRerF: ",signif(amCal[2,2], digits=2),"\nXGBoost: ", signif(amCal[4,2], digits=2), "\nRanger: ", signif(amCal[5,2],digits=2))))
}
```
