---
title: "Test speed-up and scale-up of R-Rerf Iteration 8"
author: "James Browne"
date: "May 16 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = FALSE)
library(ggplot2)
library(reshape)
 library(scales)
library(plyr)
library(randomForest)
library(ranger)
library(xgboost)
library(rerf)

leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))

runRerF <- TRUE
runXG <- TRUE
runRF <- TRUE
runRanger <- TRUE
nTimes <- 10
num_trees <-  100
median_time <- NA
num.threads <- 20
data <- data.frame()
```


**********************************************************************
#### Loading the images and labels
**********************************************************************
```{r LoadView, cache = FALSE}
#Size of the labels is 1 whereas everything else is 4
#Open and position the image file
image_block <- file("../../data/ubyte/train-images-idx3-ubyte", "rb")
q <- readBin(image_block, integer(), n=1, endian="big")
num_images <- readBin(image_block, integer(), n=1, endian="big")
num_col <- readBin(image_block, integer(), n=1, endian="big")
num_row <- readBin(image_block, integer(), n=1, endian="big")

#Open and position the label file
label_block = file("../../data/ubyte/train-labels-idx1-ubyte", "rb")
q <- readBin(label_block, integer(), n=1, endian="big")
num_labels <- readBin(label_block, integer(), n=1, endian="big")

X <- readBin(image_block, integer(), n=num_images*num_col*num_row, size=1, signed=FALSE)
X <- matrix(X, ncol=num_col*num_row, byrow=TRUE)

Y <- as.numeric(readBin(label_block, integer(), n=num_labels, size=1, signed=FALSE)+1)

close(image_block)
close(label_block)

image_block <- file("../../data/ubyte/t10k-images-idx3-ubyte", "rb")
q <- readBin(image_block, integer(), n=1, endian="big")
num_images <- readBin(image_block, integer(), n=1, endian="big")
num_col <- readBin(image_block, integer(), n=1, endian="big")
num_row <- readBin(image_block, integer(), n=1, endian="big")

#Open and position the label file
label_block = file("../../data/ubyte/t10k-labels-idx1-ubyte", "rb")
q <- readBin(label_block, integer(), n=1, endian="big")
num_labels <- readBin(label_block, integer(), n=1, endian="big")

Xt <- readBin(image_block, integer(), n=num_images*num_col*num_row, size=1, signed=FALSE)
Xt <- matrix(Xt, ncol=num_col*num_row, byrow=TRUE)

Yt <- as.numeric(readBin(label_block, integer(), n=num_labels, size=1, signed=FALSE)+1)

close(image_block)
close(label_block)
image_block <- NULL
label_block <- NULL

gc()

NameResults <- "MNIST"
Results <- NULL
Alg <- NULL
```

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r MNIST_RerF, cache = FALSE}
#create impossible dataset
if(runRerF){
ptm_hold <- NA
for (i in 1:nTimes){
    gc()

    forest <- RerF(X,Y, trees=num_trees, bagging=.3, min.parent=1, max.depth=0, store.oob=TRUE, stratify=TRUE, num.cores=num.threads, seed=sample(1:100000,1) )
    predictions <- Predict(Xt, forest, num.cores = num.threads)
    error.rate <- mean(predictions != Yt)
    ptm_hold[i] <- error.rate
}
Results <- c(Results, ptm_hold)
Alg <- c(Alg, rep("RerF", nTimes))
}
```

```{r MNIST_XGBoost, cache = FALSE}
#create impossible dataset
if(runXG){
num_classes <- length(unique(Y))
train <- apply(X,2,as.numeric)
label <- Y-1
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
            forest <- xgboost(data=train, label=label, objective="multi:softprob", nrounds=num_trees,num_class=num_classes, nthread=num.threads)
testS <- apply(Xt,2,as.numeric)
testlabel <- Yt-1

pred <- predict(forest, testS) 
pred <- matrix(pred, ncol=num_classes, byrow=TRUE) 
pred_labels <- max.col(pred) - 1
     error.rate <- mean(pred_labels != testlabel)

			ptm_hold[i] <- error.rate
		}
        Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("XGBoost",nTimes))
}
```

```{r MNIST_RandomForest, cache = FALSE}
#create impossible dataset
if(runRF){
Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			forest <- randomForest(X,Yrf, ntree=num_trees)
pred <- predict(forest, Xt)
     error.rate <- mean(pred != as.factor(as.character(Yt)))
			ptm_hold[i] <- error.rate
		}
Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("RF", nTimes))

}
```

```{r MNIST_Ranger, cache = FALSE}
#create impossible dataset
if(runRanger){
X <- cbind(X,Y)
colnames(X) <- as.character(1:ncol(X))

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
            forest <- ranger(dependent.variable.name = as.character(ncol(X)), data = X, num.trees = num_trees, num.threads = num.threads, classification=TRUE)
colnames(Xt) <- as.character(1:ncol(Xt))
pred <- predict(forest,Xt)
     error.rate <- mean(pred$predictions != Yt)
			ptm_hold[i] <- error.rate
		}
        Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("Ranger", nTimes))
}
```

```{r MNIST_process, cache = FALSE}
data <- rbind(data, Results)
```

**********************************************************************
#### Loading Higgs
**********************************************************************
```{r LoadViewHiggs, cache = FALSE}
mydata <- read.csv(file="../../data/higgs/training.csv", header=TRUE, sep=",")
X <- as.matrix(mydata[,2:31])
Y <- as.numeric(mydata[,33])
mydata <- NA
gc()

NameResults <- c(NameResults, "Higgs")
Results <- NULL
Alg <- NULL
```

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r Higgs_RerF, cache = FALSE}
if(runRerF){
#create impossible dataset
		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1,][X1,],X[Y==2,][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1,][-X1,],X[Y==2,][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])

			gc()
			forest <- RerF(Xtr,Ytr, trees=num_trees, bagging=.3, min.parent=1, max.depth=0, store.oob=TRUE, stratify=TRUE, num.cores=ceiling(num.threads/5),seed=sample(1:100000,1))
            for( q in 1:num_trees){
m <- which(is.na(forest$trees[[q]]$ClassProb))
forest$trees[[q]]$ClassProb[m] <- .5
            }
predictions <- Predict(Xte, forest, num.cores =num.threads)
     error.rate <- mean(predictions != Yte)
			ptm_hold[i] <- error.rate
		}
        
        Results <- c(Results, ptm_hold)
Alg <- c(Alg, rep("RerF", nTimes))
}
```

```{r Higgs_XGBoost, cache = FALSE}
#create impossible dataset
if(runXG){
num_classes <- length(unique(Y))
train <- apply(X,2,as.numeric)
label <- Y-1

		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1,][X1,],X[Y==2,][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1,][-X1,],X[Y==2,][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
train <- apply(Xtr,2,as.numeric)
label <- Ytr-1
			gc()
            forest <- xgboost(data=train, label=label, objective="multi:softprob",nrounds=num_trees,max_depth=30000, num_class=num_classes, nthread=num.threads)
testS <- apply(Xte,2,as.numeric)
testlabel <- Yte-1
pred <- predict(forest, testS) 
pred <- matrix(pred, ncol=num_classes, byrow=TRUE)
pred_labels <- max.col(pred) - 1
     error.rate <- mean(pred_labels != testlabel)

			ptm_hold[i] <-error.rate 
		}
Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("XGBoost",nTimes))
}
```

```{r Higgs_RandomForest, cache = FALSE}
#create impossible dataset
if(runRF){

#Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1,][X1,],X[Y==2,][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1,][-X1,],X[Y==2,][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
Yrf<-as.factor(as.character(Ytr))

			gc()
			forest <- randomForest(Xtr,Yrf, ntree=num_trees)
pred <- predict(forest, Xte)
     error.rate <- mean(pred != as.factor(as.character(Yte)))
			ptm_hold[i] <- error.rate
		}
Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("RF", nTimes))
}
```

```{r Higgs_Ranger, cache = FALSE}
#create impossible dataset
if(runRanger){
#X <- cbind(X,Y)
#colnames(X) <- as.character(1:ncol(X))


		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1,][X1,],X[Y==2,][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1,][-X1,],X[Y==2,][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
Xtr <- cbind(Xtr, Ytr)
colnames(Xtr) <- as.character(1:ncol(Xtr))

			gc()
            forest <- ranger(dependent.variable.name = as.character(ncol(Xtr)), data = Xtr, num.trees = num_trees, num.threads =num.threads, classification=TRUE)
ptm <- proc.time()
colnames(Xte) <- as.character(1:ncol(Xte))
pred <- predict(forest,Xte)

     error.rate <- mean(pred$predictions != Yte)
			ptm_hold[i] <- error.rate
		}
Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("Ranger", nTimes))
}
```


```{r Higgs_process, cache = FALSE}
data <- rbind(data, Results)
```


```{r LoadViewp53, cache = FALSE}
mydata <- read.csv(file="../../data/p53.csv", header=TRUE, sep=",")
X <- as.matrix(mydata[,1:(ncol(mydata)-1)])
Y <- as.numeric(mydata[,ncol(mydata)])
mydata <- NA
gc()

NameResults <- c(NameResults, "p53")
Results <- NULL
Alg <- NULL
```

```{r p53_RerF, cache = FALSE}
#create impossible dataset
if(runRerF){
		ptm_hold <- NA
		for (i in 1:nTimes){
            X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1,][X1,],X[Y==2,][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1,][-X1,],X[Y==2,][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
			gc()
			forest <- RerF(Xtr,Ytr, trees=num_trees, bagging=.3, min.parent=1, max.depth=0, store.oob=TRUE, stratify=TRUE, num.cores=num.threads,seed=sample(1:100000,1))
predictions <- Predict(Xte, forest, num.cores = num.threads)
     error.rate <- mean(predictions != Yte)
			ptm_hold[i] <- error.rate
		}
        
        Results <- c(Results, ptm_hold)
Alg <- c(Alg, rep("RerF", nTimes))
}
```

```{r p53_XGBoost, cache = FALSE}
#create impossible dataset
if(runXG){
num_classes <- length(unique(Y))

		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1,][X1,],X[Y==2,][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1,][-X1,],X[Y==2,][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
train <- apply(Xtr,2,as.numeric)
label <- Ytr-1

			gc()
            forest <- xgboost(data=train, label=label, objective="multi:softprob",nrounds=num_trees,max_depth=30000, num_class=num_classes, nthread=num.threads)
testS <- apply(Xte,2,as.numeric)
testlabel <- Yte-1
pred <- predict(forest, testS) 
pred <- matrix(pred, ncol=num_classes, byrow=TRUE)
pred_labels <- max.col(pred) - 1
     error.rate <- mean(pred_labels != testlabel)
			ptm_hold[i] <- error.rate
		}
Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("XGBoost",nTimes))
}
```

```{r p53_RandomForest, cache = FALSE}
#create impossible dataset
if(runRF){

#Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1,][X1,],X[Y==2,][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1,][-X1,],X[Y==2,][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
Yrf<-as.factor(as.character(Ytr))

			gc()
			forest <- randomForest(Xtr,Yrf, ntree=num_trees)
pred <- predict(forest, Xte)
     error.rate <- mean(pred != as.factor(as.character(Yte)))
			ptm_hold[i] <-error.rate
		}
Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("RF", nTimes))
}
```

```{r p53_Ranger, cache = FALSE}
if(runRanger){
		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1,][X1,],X[Y==2,][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1,][-X1,],X[Y==2,][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
Xtr <- cbind(Xtr, Ytr)
colnames(Xtr) <- as.character(1:ncol(Xtr))
			gc()
            forest <- ranger(dependent.variable.name = as.character(ncol(Xtr)), data = Xtr, num.trees = num_trees, num.threads =num.threads, classification=TRUE)
colnames(Xte) <- as.character(1:ncol(Xte))
pred <- predict(forest,Xte)
     error.rate <- mean(pred$predictions != Yte)
			ptm_hold[i] <-error.rate
		}
Results <- c(Results, ptm_hold)
        Alg <- c(Alg, rep("Ranger", nTimes))
}
```


```{r p53_process, cache = FALSE}
data <- rbind(data, Results)
```


```{r print_test, cache = FALSE}
ress1 <- cbind(NameResults,data)
colnames(ress1) <- c("Dataset", Alg)

ress1 <- melt(ress1, id.vars='Dataset')
save(ress1, file="accuracy.Rdata")


print(g <- ggplot(ress1, aes(Dataset, value,color = variable)) + geom_point(position=position_jitterdodge(dodge.width=0.5))+ leg + labs(title="Error Rates", x="Dataset", y="Average Error Rate ", subtitle=paste("")))
```
