---
title: "Test speed-up and scale-up of R-Rerf Iteration 8"
author: "James Browne"
date: "May 16 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = FALSE)
library(ggplot2)
library(reshape)
 library(scales)
library(plyr)
library(randomForest)

leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))


nTimes <-20
num_trees <- 100  
median_time <- NA
data <- data.frame()
```


**********************************************************************
#### Loading the images and labels
**********************************************************************
```{r LoadView, cache = FALSE}
#Size of the labels is 1 whereas everything else is 4
#Open and position the image file
image_block <- file("../../data/ubyte/train-images-idx3-ubyte", "rb")
q <- readBin(image_block, integer(), n=1, endian="big")
num_images <- readBin(image_block, integer(), n=1, endian="big")
num_col <- readBin(image_block, integer(), n=1, endian="big")
num_row <- readBin(image_block, integer(), n=1, endian="big")

#Open and position the label file
label_block = file("../../data/ubyte/train-labels-idx1-ubyte", "rb")
q <- readBin(label_block, integer(), n=1, endian="big")
num_labels <- readBin(label_block, integer(), n=1, endian="big")

X <- readBin(image_block, integer(), n=num_images*num_col*num_row, size=1, signed=FALSE)
X <- matrix(X, ncol=num_col*num_row, byrow=TRUE)

Y <- as.numeric(readBin(label_block, integer(), n=num_labels, size=1, signed=FALSE)+1)

close(image_block)
close(label_block)
Xr <- as.matrix(replicate(784,rnorm(60000)))
	Yr <- as.numeric(sample(1:10, 60000, replace=TRUE))
gc()

NameResults <- "MNIST"
Results <- NULL
Alg <- NULL
```

Testing R-Rerf iter10 on growing easy and impossible(random) datasets.  Testing time and memory.

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r MNIST_RerF, cache = FALSE}
#create impossible dataset
if(exists("comp_rfr")){
  rm(comp_rfr, rfr)
  }
source('../../code/rfr_function.R')

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- rfr(X,Y, trees=num_trees, bagging=.3, MinParent=1, MaxDepth="inf", COOB=TRUE, stratify=TRUE, NumCores=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        Results <- c(Results, median(ptm_hold))
        Alg <- c(Alg, "RerF")
```

```{r MNIST_RerF_Row, cache = FALSE}
#create impossible dataset
if(exists("comp_rfr")){
  rm(comp_rfr, rfr)
  }
source('code/rfr_function.R')
Xrf <- as.matrix(X, byrow=TRUE)
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- rfr(Xrf,Y, trees=num_trees, bagging=.3, MinParent=1, MaxDepth="inf", COOB=TRUE, stratify=TRUE, NumCores=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        Results <- c(Results, median(ptm_hold))
        Alg <- c(Alg, "RerF(row)")
```

```{r MNIST_RerF_breadth, cache = FALSE}
#create impossible dataset
if(exists("comp_rfr")){
  rm(comp_rfr, rfr)
  }
source('../../code/brfr.R')

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- rfr(X,Y, trees=num_trees, bagging=.3, MinParent=1, MaxDepth="inf", COOB=TRUE, stratify=TRUE, NumCores=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        Results <- c(Results, median(ptm_hold))
        Alg <- c(Alg, "RerF(breadth)")
```

```{r MNIST_RandomForest, cache = FALSE}
#create impossible dataset
if(TRUE){
if(exists("comp_rfr")){
  rm(comp_rfr, rfr)
  }
Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- randomForest(X,Yrf, ntree=num_trees)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold))
        Alg <- c(Alg, "RF")

}
```

```{r MNIST_process, cache = FALSE}
data <- rbind(data, Results)
```

**********************************************************************
#### Loading Higgs
**********************************************************************
```{r LoadViewHiggs, cache = FALSE}
mydata <- read.csv(file="../../data/higgs/training.csv", header=TRUE, sep=",")
X <- as.matrix(mydata[,2:32])
Y <- as.numeric(mydata[,33])
mydata <- NA
gc()

NameResults <- c(NameResults, "Higgs")
Results <- NULL
Alg <- NULL
```

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r Higgs_RerF, cache = FALSE}
#create impossible dataset
if(exists("comp_rfr")){
  rm(comp_rfr, rfr)
  }
source('../../code/rfr_function.R')

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- rfr(X,Y, trees=num_trees, bagging=.3, MinParent=1, MaxDepth="inf", COOB=TRUE, stratify=TRUE, NumCores=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        
        Results <- c(Results, median(ptm_hold))
        Alg <- c(Alg, "RerF")
```

```{r Higgs_RerF_Row, cache = FALSE}
#create impossible dataset
if(exists("comp_rfr")){
  rm(comp_rfr, rfr)
  }
source('code/rfr_function.R')

		ptm_hold <- NA
Xrf <- as.matrix(X, byrow=TRUE)
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- rfr(Xrf,Y, trees=num_trees, bagging=.3, MinParent=1, MaxDepth="inf", COOB=TRUE, stratify=TRUE, NumCores=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold))
        Alg <- c(Alg, "RerF(row)")
```

```{r Higgs_RerF_breadth, cache = FALSE}
#create impossible dataset
if(exists("comp_rfr")){
  rm(comp_rfr, rfr)
  }
source('../../code/brfr.R')

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- rfr(X,Y, trees=num_trees, bagging=.3, MinParent=1, MaxDepth="inf", COOB=TRUE, stratify=TRUE, NumCores=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold))
        Alg <- c(Alg, "RerF(breadth)")
```

```{r Higgs_RandomForest, cache = FALSE}
#create impossible dataset
if(TRUE){
if(exists("comp_rfr")){
  rm(comp_rfr, rfr)
  }
Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- randomForest(X,Yrf, ntree=num_trees)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold))
        Alg <- c(Alg, "RF")
}
```

```{r Higgs_process, cache = FALSE}
data <- rbind(data, Results)
```


```{r print_test, cache = FALSE}
ress1 <- cbind(NameResults,data)
colnames(ress1) <- c("Dataset", Alg)

#ress1<-data.frame(Dataset=as.factor(dataset), Time_Sec=median_time, Line_Type = as.factor(line_type))
ress1 <- melt(ress1, id.vars='Dataset')
save(ress1, file="speed.Rdata")

print(g <- ggplot(ress1, aes(Dataset, value)) + geom_bar(aes(fill = variable), position = "dodge", stat="identity"))
#print(ggplot(ress2,aes(x=Cores_Used, y=Scale_Up, group=Line_Type, color=Line_Type))+geom_line()+labs(title="R-RerF Scale-Up", x="Number of Cores", y="Scale-Up", subtitle=paste("Initial number of samples: ", baseS))+expand_limits(y=c(0,1))+leg)
```
