---
title: "Test speed-up and scale-up of R-Rerf Iteration 8"
author: "James Browne"
date: "May 16 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = FALSE)
source('rfr_function.R')
library(ggplot2)
nTimes <-20
leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))
run_su <-TRUE 
run_scu <-TRUE #FALSE
```


**********************************************************************
#### Loading the images and labels
**********************************************************************
```{r LoadView, cache = FALSE}
#Size of the labels is 1 whereas everything else is 4
#Open and position the image file
image_block <- file("../../data/ubyte/train-images-idx3-ubyte", "rb")
q <- readBin(image_block, integer(), n=1, endian="big")
num_images <- readBin(image_block, integer(), n=1, endian="big")
num_col <- readBin(image_block, integer(), n=1, endian="big")
num_row <- readBin(image_block, integer(), n=1, endian="big")

#Open and position the label file
label_block = file("../../data/ubyte/train-labels-idx1-ubyte", "rb")
q <- readBin(label_block, integer(), n=1, endian="big")
num_labels <- readBin(label_block, integer(), n=1, endian="big")

X <- readBin(image_block, integer(), n=num_images*num_col*num_row, size=1, signed=FALSE)
X <- matrix(X, ncol=num_col*num_row, byrow=TRUE)

Y <- as.numeric(readBin(label_block, integer(), n=num_labels, size=1, signed=FALSE)+1)

close(image_block)
close(label_block)
gc()
```

Testing R-Rerf iter10 on growing easy and impossible(random) datasets.  Testing time and memory.

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r speed_up, cache = FALSE}
#create impossible dataset
num_trees <-64 
line_type <- NA
cores_used <- NA
median_time <- NA
speed_up <- NA
entry <-1
numS<-20000
ML <- 6
initial_run_entry<-entry
data_size_curr <- (object.size(X[1:numS,])+object.size(Y[1:numS]))/1000000
if(run_su){
		for (p in 2:ML){
		q <- 2^(p-1)
		ptm_hold <- NA
		forest_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- rfr(X[1:numS,],Y[1:numS], trees=num_trees, bagging=.3, MinParent=1, MaxDepth="inf", COOB=TRUE, stratify=TRUE, NumCores=q)
			ptm_hold[i] <- (proc.time() - ptm)[3]
			forest[i] <- object.size(forest)
		}
		line_type[entry]<-"MNIST (20000x784)"
		cores_used[entry] <- q
		median_time[entry]<- median(ptm_hold)
		speed_up[entry]<-2*median_time[initial_run_entry]/median_time[entry]
        entry<-entry+1
	}

for (p in 2:ML){
	q<- 2^(p-1)
	line_type[entry]<-"Ideal"
	cores_used[entry] <- q
	median_time[entry]<-2 
	speed_up[entry]<- q
    entry<-entry+1
}
}
ress1<-data.frame(Line_Type=as.factor(line_type), Cores_Used = as.factor(cores_used), Time_Sec=median_time, Speed_Up=speed_up)
```

```{r speed_up_print, cache = FALSE}
if(run_su){
save(ress1, file="exp0002speedUp.Rdata")
amCalcSU<-(2^speed_up[4])/(2^speed_up[5])
cat("Amdahl's Number: ", 1/((1-amCalcSU)+(amCalcSU/2)), "\n")
cat("Dataset Size: ", data_size_curr ,"MB\n")
cat(numS, " samples from the MNIST dataset")
lab <- labs(title="R-RerF Strong Scaling", x="Number of Cores", y="Relative Performance", subtitle =paste("Dataset Size: ", data_size_curr, "MB"))
print(ggplot(ress1,aes(x=Cores_Used, y=Speed_Up, group=Line_Type, color=Line_Type))+geom_line()+lab +leg +scale_y_continuous(trans = "log2", breaks = c(1,2,4,8,16,32)))

gc()
}
```


**********************************************************************
#### Scale-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Scale Up, proportional increase in resource (number of samples and cores).  
**********************************************************************
```{r scale-up-n, cache = FALSE}
#create impossible dataset
#X <- as.matrix(replicate(32,rnorm(60000)))
#Y <- as.numeric(sample(1:4, 60000, replace=TRUE))
num_trees <-64 
data_size <- NA
cores_used <- NA
median_time <- NA
scale_up <- NA
entry <- 1
line_type <- NA
baseS <- 2500
facE <- 1.72
facEX<-c(1,1.75,1.76,1.77,1.78,1.79,1.8) #for nlog2(n)
#facEX<-c(1,1.86,1.87,1.87,1.88,1.89,1.89) #for nlog(n)
facE2 <- 1.83
data_size_curr <- (object.size(X[1:baseS,])+object.size(Y[1:baseS]))/1000000
initial_run_entry<-entry
if (run_scu){
    facm <- baseS
for (m in 2:6){
    facm <- facm*facEX[m-1]
numS <- floor(facm)
		q <- 2^(m-1)
		ptm_hold <- NA
		forest_hold <- NA
		for (i in 1:nTimes){
			ptm <- proc.time()
			forest <- rfr(X[1:numS,],Y[1:numS], trees=num_trees, bagging=0, MinParent=1, MaxDepth="inf",COOB=TRUE, stratify=TRUE, NumCores=q)
			ptm_hold[i] <- (proc.time() - ptm)[3]
			forest[i] <- object.size(forest)
		}
line_type[entry] <- "MNIST"
		cores_used[entry] <- q
		median_time[entry]<- median(ptm_hold)
		scale_up[entry]<-median_time[initial_run_entry]/median_time[entry] 
		entry = entry+1
line_type[entry] <- "Ideal"
		cores_used[entry] <- q
		median_time[entry]<- median(ptm_hold)
		scale_up[entry]<-1 
		entry = entry+1
}
}
ress2<-data.frame(Line_Type=as.factor(line_type), Cores_Used = as.factor(cores_used), Time_Sec=median_time, Scale_Up=scale_up)
```

```{r scale-up-n_print, cache = FALSE}
if (run_scu){
save(ress2, file="exp0002scaleUp.Rdata")
Tics <- scale_y_continuous(breaks=c(0.0,0.5,1.0),labels=c(0.0,0.5,1.0))
print(ggplot(ress2,aes(x=Cores_Used, y=Scale_Up, group=Line_Type, color=Line_Type))+geom_line()+labs(title="R-RerF Weak Scaling", x="Number of Cores", y="Relative Performance", subtitle=paste("Initial number of samples: ", baseS,"; Ideal assumes average case complexity"))+expand_limits(y=c(0,1))+leg)
}
gc()
```
