---
title: "Test Training Speed of several Forest Algorithms"
author: "James Browne"
date: "Oct 10 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = FALSE)
library(ggplot2)
library(reshape)
 library(scales)
library(plyr)
library(randomForest)
library(ranger)
library(xgboost)
source("tyler.R")

leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))


nTimes <- 10
num_trees <- 50
median_time <- NA
data <- data.frame()
```


**********************************************************************
#### Loading the images and labels
**********************************************************************
```{r LoadView, cache = FALSE}
#Size of the labels is 1 whereas everything else is 4
#Open and position the image file
image_block <- file("../../data/ubyte/train-images-idx3-ubyte", "rb")
q <- readBin(image_block, integer(), n=1, endian="big")
num_images <- readBin(image_block, integer(), n=1, endian="big")
num_col <- readBin(image_block, integer(), n=1, endian="big")
num_row <- readBin(image_block, integer(), n=1, endian="big")

#Open and position the label file
label_block = file("../../data/ubyte/train-labels-idx1-ubyte", "rb")
q <- readBin(label_block, integer(), n=1, endian="big")
num_labels <- readBin(label_block, integer(), n=1, endian="big")

X <- readBin(image_block, integer(), n=num_images*num_col*num_row, size=1, signed=FALSE)
X <- matrix(X, ncol=num_col*num_row, byrow=TRUE)

Y <- as.numeric(readBin(label_block, integer(), n=num_labels, size=1, signed=FALSE)+1)

close(image_block)
close(label_block)
Xr <- as.matrix(replicate(784,rnorm(60000)))
	Yr <- as.numeric(sample(1:10, 60000, replace=TRUE))
gc()

NameResults <- "MNIST"
Results <- NULL
Alg <- NULL
```

Testing R-Rerf iter10 on growing easy and impossible(random) datasets.  Testing time and memory.

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r MNIST_RerF, cache = FALSE}
#create impossible dataset


		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()

			forest <- rerf(X,Y, trees=num_trees, bagging=.3, MinParent=1, MaxDepth=0, COOB=TRUE, stratify=TRUE, NumCores=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        Results <- c(Results, median(ptm_hold)/num_trees)
        Alg <- c(Alg, "RerF")
```

```{r MNIST_XGBoost, cache = FALSE}
#create impossible dataset
if(FALSE){
num_classes <- length(unique(Y))
train <- apply(X,2,as.numeric)
label <- Y-1
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
            forest <- xgboost(data=train, label=label, objective="multi:softprob",nrounds=num_trees,max_depth=30000, num_class=num_classes, nthread=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        Results <- c(Results, median(ptm_hold)/num_trees)
        Alg <- c(Alg, "XGBoost")
}
```

```{r MNIST_Ranger, cache = FALSE}
#create impossible dataset
X <- cbind(X,Y)
colnames(X) <- as.character(1:ncol(X))

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
            forest <- ranger(dependent.variable.name = as.character(ncol(X)), data = X, num.trees = num_trees, num.threads = 1, classification=TRUE)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        Results <- c(Results, median(ptm_hold)/num_trees)
        Alg <- c(Alg, "Ranger")
```

```{r MNIST_RandomForest, cache = FALSE}
#create impossible dataset
if(TRUE){
Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- randomForest(X,Yrf, ntree=num_trees)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees)
        Alg <- c(Alg, "RF")

}
```

```{r MNIST_process, cache = FALSE}
data <- rbind(data, Results)
```

**********************************************************************
#### Loading Higgs
**********************************************************************
```{r LoadViewHiggs, cache = FALSE}
mydata <- read.csv(file="../../data/higgs/training.csv", header=TRUE, sep=",")
X <- as.matrix(mydata[,2:32])
Y <- as.numeric(mydata[,33])
mydata <- NA
gc()

NameResults <- c(NameResults, "Higgs")
Results <- NULL
Alg <- NULL
```

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r Higgs_RerF, cache = FALSE}
#create impossible dataset
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- rerf(X,Y, trees=num_trees, bagging=.3, MinParent=1, MaxDepth=0, COOB=TRUE, stratify=TRUE, NumCores=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        
        Results <- c(Results, median(ptm_hold)/num_trees)
        Alg <- c(Alg, "RerF")
```

```{r Higgs_XGBoost, cache = FALSE}
#create impossible dataset
if(FALSE){
num_classes <- length(unique(Y))
train <- apply(X,2,as.numeric)
label <- Y-1

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
            forest <- xgboost(data=train, label=label, objective="multi:softprob",nrounds=num_trees,max_depth=30000, num_class=num_classes, nthread=1)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees)
        Alg <- c(Alg, "XGBoost")
}
```

```{r Higgs_Ranger, cache = FALSE}
#create impossible dataset
X <- cbind(X,Y)
colnames(X) <- as.character(1:ncol(X))


		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
            forest <- ranger(dependent.variable.name = as.character(ncol(X)), data = X, num.trees = num_trees, num.threads = 1, classification=TRUE)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees)
        Alg <- c(Alg, "Ranger")
```

```{r Higgs_RandomForest, cache = FALSE}
#create impossible dataset
if(TRUE){

Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			ptm <- proc.time()
			forest <- randomForest(X,Yrf, ntree=num_trees)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees)
        Alg <- c(Alg, "RF")
}
```

```{r Higgs_process, cache = FALSE}
data <- rbind(data, Results)
```


```{r print_test, cache = FALSE}
ress1 <- cbind(NameResults,data)
colnames(ress1) <- c("Dataset", Alg)

ress1 <- melt(ress1, id.vars='Dataset')
save(ress1, file="speedSXG.Rdata")

leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))

print(g <- ggplot(ress1, aes(Dataset, value)) + geom_bar(aes(fill = variable), position = "dodge", stat="identity") + leg + labs(title="Algorithm Training Times", x="Dataset", y="Per Tree Training Time (s)", subtitle=paste("")))
#print(ggplot(ress2,aes(x=Cores_Used, y=Scale_Up, group=Line_Type, color=Line_Type))+geom_line()+labs(title="R-RerF Scale-Up", x="Number of Cores", y="Scale-Up", subtitle=paste("Initial number of samples: ", baseS))+expand_limits(y=c(0,1))+leg)
```
