---
title: "Test speed-up and scale-up of R-Rerf Iteration 8"
author: "James Browne"
date: "May 16 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = FALSE)
library(ggplot2)
library(reshape)
 library(scales)
library(plyr)
library(randomForest)
library(ranger)
library(xgboost)
library(rerf)

leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))


nTimes <- 2
num_trees <- 2  
median_time <- NA
data <- data.frame()
```

**********************************************************************
#### Loading Higgs
**********************************************************************
```{r LoadViewHiggs, cache = FALSE}
mydata <- read.csv(file="../../data/higgs/training.csv", header=TRUE, sep=",")
X <- as.matrix(mydata[,2:31])
Y <- as.numeric(mydata[,33])
mydata <- read.csv(file="../../data/higgs/test.csv", header=TRUE, sep=",")
```
```{r LoadViewHiggs2, cache = FALSE}
mydata <- read.csv(file="../../data/higgs/test.csv", header=TRUE, sep=",")
Xt <- as.matrix(mydata[,2:31])
#Yt <- as.numeric(mydata[,33])
mydata <- NA
gc()

NameResults <-"Higgs" 
Results <- NULL
Alg <- NULL
```

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r Higgs_RerF, cache = FALSE}
#create impossible dataset
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			forest <- RerF(X,Y, trees=num_trees, bagging=.3, min.parent=1, max.depth=0, store.oob=TRUE, stratify=TRUE, num.cores=1)
ptm <- proc.time()
predictions <- Predict(Xt, forest, num.cores = 1L)
#     error.rate <- mean(predictions != Yt)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        
        Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xt))
        Alg <- c(Alg, "RerF")
```

```{r Higgs_XGBoost, cache = FALSE}
#create impossible dataset
num_classes <- length(unique(Y))
train <- apply(X,2,as.numeric)
label <- Y-1

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
            forest <- xgboost(data=train, label=label, objective="multi:softprob",nrounds=num_trees,max_depth=30000, num_class=num_classes, nthread=1)
train <- apply(Xt,2,as.numeric)
label <- Yt-1

ptm <- proc.time()
pred <- predict(forest, train) 
#     error.rate <- mean(pred != label)

			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xt))
        Alg <- c(Alg, "XGBoost")
```

```{r Higgs_RandomForest, cache = FALSE}
#create impossible dataset
if(TRUE){

Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			forest <- randomForest(X,Yrf, ntree=num_trees)
ptm <- proc.time()
pred <- randomForest::predict(forest, Xt)
#     error.rate <- mean(pred != as.factor(as.character(Yt)))
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xt))
        Alg <- c(Alg, "RF")
}
```

```{r Higgs_Ranger, cache = FALSE}
#create impossible dataset
X <- cbind(X,Y)
colnames(X) <- as.character(1:ncol(X))


		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
            forest <- ranger(dependent.variable.name = as.character(ncol(X)), data = X, num.trees = num_trees, num.threads = 1, classification=TRUE)
ptm <- proc.time()
colnames(Xt) <- as.character(1:ncol(Xt))
pred <- predict(forest,Xt)

#     error.rate <- mean(pred != Yt)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xt))
        Alg <- c(Alg, "Ranger")
```


```{r Higgs_process, cache = FALSE}
data <- rbind(data, Results)
```


**********************************************************************
#### Loading the images and labels
**********************************************************************
```{r LoadView, cache = FALSE}
#Size of the labels is 1 whereas everything else is 4
#Open and position the image file
image_block <- file("../../data/ubyte/train-images-idx3-ubyte", "rb")
q <- readBin(image_block, integer(), n=1, endian="big")
num_images <- readBin(image_block, integer(), n=1, endian="big")
num_col <- readBin(image_block, integer(), n=1, endian="big")
num_row <- readBin(image_block, integer(), n=1, endian="big")

#Open and position the label file
label_block = file("../../data/ubyte/train-labels-idx1-ubyte", "rb")
q <- readBin(label_block, integer(), n=1, endian="big")
num_labels <- readBin(label_block, integer(), n=1, endian="big")

X <- readBin(image_block, integer(), n=num_images*num_col*num_row, size=1, signed=FALSE)
X <- matrix(X, ncol=num_col*num_row, byrow=TRUE)

Y <- as.numeric(readBin(label_block, integer(), n=num_labels, size=1, signed=FALSE)+1)


close(image_block)
close(label_block)

image_block <- file("../../data/ubyte/t10k-images-idx3-ubyte", "rb")
q <- readBin(image_block, integer(), n=1, endian="big")
num_images <- readBin(image_block, integer(), n=1, endian="big")
num_col <- readBin(image_block, integer(), n=1, endian="big")
num_row <- readBin(image_block, integer(), n=1, endian="big")

#Open and position the label file
label_block = file("../../data/ubyte/t10k-labels-idx1-ubyte", "rb")
q <- readBin(label_block, integer(), n=1, endian="big")
num_labels <- readBin(label_block, integer(), n=1, endian="big")

Xt <- readBin(image_block, integer(), n=num_images*num_col*num_row, size=1, signed=FALSE)
Xt <- matrix(X, ncol=num_col*num_row, byrow=TRUE)

Yt <- as.numeric(readBin(label_block, integer(), n=num_labels, size=1, signed=FALSE)+1)

close(image_block)
close(label_block)

gc()

NameResults <- c(NameResults, "MNIST")
Results <- NULL
Alg <- NULL
```

Testing R-Rerf iter10 on growing easy and impossible(random) datasets.  Testing time and memory.

**********************************************************************
#### Speed-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Speed-up: testing time reduction as number of cores grows.  
**********************************************************************
```{r MNIST_RerF, cache = FALSE}
#create impossible dataset
ptm_hold <- NA
for (i in 1:nTimes){
    gc()

    forest <- RerF(X,Y, trees=num_trees, bagging=.3, min.parent=1, max.depth=6, store.oob=TRUE, stratify=TRUE, num.cores=1)
    ptm <- proc.time()
    predictions <- Predict(Xt, forest, num.cores = 1L)
    error.rate <- mean(predictions != Yt)
    ptm_hold[i] <- (proc.time() - ptm)[3]
}
Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xt))
Alg <- c(Alg, "RerF")
```

```{r MNIST_XGBoost, cache = FALSE}
#create impossible dataset
num_classes <- length(unique(Y))
train <- apply(X,2,as.numeric)
label <- Y-1
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
            forest <- xgboost(data=train, label=label, objective="multi:softprob", nrounds=num_trees,num_class=num_classes, nthread=1)
train <- apply(Xt,2,as.numeric)
label <- Yt-1

ptm <- proc.time()
pred <- predict(forest, train) 
     error.rate <- mean(pred != label)

			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xt))
        Alg <- c(Alg, "XGBoost")
```

```{r MNIST_RandomForest, cache = FALSE}
#create impossible dataset
if(TRUE){
Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
			forest <- randomForest(X,Yrf, ntree=num_trees)
ptm <- proc.time()
pred <- randomForest::predict(forest, Xt)
     error.rate <- mean(pred != as.factor(as.character(Yt)))
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xt))
        Alg <- c(Alg, "RF")

}
```

```{r MNIST_Ranger, cache = FALSE}
#create impossible dataset
X <- cbind(X,Y)
colnames(X) <- as.character(1:ncol(X))

		ptm_hold <- NA
		for (i in 1:nTimes){
			gc()
            forest <- ranger(dependent.variable.name = as.character(ncol(X)), data = X, num.trees = num_trees, num.threads = 1, classification=TRUE)
ptm <- proc.time()
colnames(Xt) <- as.character(1:ncol(Xt))
pred <- predict(forest,Xt)
     error.rate <- mean(pred != Yt)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xt))
        Alg <- c(Alg, "Ranger")
```



```{r MNIST_process, cache = FALSE}
data <- rbind(data, Results)
```



```{r LoadViewp53, cache = FALSE}
mydata <- read.csv(file="../../data/p53.csv", header=TRUE, sep=",")
X <- as.matrix(mydata[,1:ncol(mydata)-1])
Y <- as.numeric(mydata[,ncol(mydata)])
mydata <- NA
gc()

NameResults <- c(NameResults, "p53")
Results <- NULL
Alg <- NULL
```

```{r p53_RerF, cache = FALSE}
#create impossible dataset
		ptm_hold <- NA
		for (i in 1:nTimes){
            X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1][X1,],X[Y==2][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1][-X1,],X[Y==2][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
			gc()
			forest <- RerF(Xtr,Ytr, trees=num_trees, bagging=.3, min.parent=1, max.depth=0, store.oob=TRUE, stratify=TRUE, num.cores=1)
ptm <- proc.time()
predictions <- Predict(Xte, forest, num.cores = 1L)
     error.rate <- mean(predictions != Yte)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
        
        Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xte))
        Alg <- c(Alg, "RerF")
```

```{r p53_XGBoost, cache = FALSE}
#create impossible dataset
num_classes <- length(unique(Y))

		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1][X1,],X[Y==2][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1][-X1,],X[Y==2][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
train <- apply(Xtr,2,as.numeric)
label <- Ytr-1

			gc()
            forest <- xgboost(data=train, label=label, objective="multi:softprob",nrounds=num_trees,max_depth=30000, num_class=num_classes, nthread=1)
train <- apply(Xte,2,as.numeric)
label <- Yte-1

ptm <- proc.time()
pred <- predict(forest, train) 
     error.rate <- mean(pred != label)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xte))
        Alg <- c(Alg, "XGBoost")
```

```{r p53_RandomForest, cache = FALSE}
#create impossible dataset
if(TRUE){

#Yrf<-as.factor(as.character(Y))
		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1][X1,],X[Y==2][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1][-X1,],X[Y==2][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
Yrf<-as.factor(as.character(Ytr))

			gc()
			forest <- randomForest(Xtr,Yrf, ntree=num_trees)
ptm <- proc.time()
pred <- randomForest::predict(forest, Xte)
     error.rate <- mean(pred != as.factor(as.character(Yte)))
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xte))
        Alg <- c(Alg, "RF")
}
```

```{r p53_Ranger, cache = FALSE}
#create impossible dataset
#X <- cbind(X,Y)
#colnames(X) <- as.character(1:ncol(X))

		ptm_hold <- NA
		for (i in 1:nTimes){
X1 <- sample(1:length(Y[Y==1]), .8 *length(Y[Y==1]), replace=FALSE)
            X2 <- sample(1:length(Y[Y==2]), .8 *length(Y[Y==2]), replace=FALSE)
            Xtr <- rbind(X[Y==1][X1,],X[Y==2][X2,])
            Ytr <- c(Y[Y==1][X1], Y[Y==2][X2])
Xte <- rbind(X[Y==1][-X1,],X[Y==2][-X2,])
            Yte <- c(Y[Y==1][-X1], Y[Y==2][-X2])
Xtr <- cbind(Xtr, Ytr)
colnames(Xtr) <- as.character(1:ncol(Xtr))
			gc()
            forest <- ranger(dependent.variable.name = as.character(ncol(Xtr)), data = Xtr, num.trees = num_trees, num.threads = 1, classification=TRUE)
ptm <- proc.time()
colnames(Xte) <- as.character(1:ncol(Xte))
pred <- predict(forest,Xte)
     error.rate <- mean(pred != Yte)
			ptm_hold[i] <- (proc.time() - ptm)[3]
		}
Results <- c(Results, median(ptm_hold)/num_trees/nrow(Xte))
        Alg <- c(Alg, "Ranger")
```


```{r p53_process, cache = FALSE}
data <- rbind(data, Results)
```


```{r print_test, cache = FALSE}
ress1 <- cbind(NameResults,data)
colnames(ress1) <- c("Dataset", Alg)

#ress1<-data.frame(Dataset=as.factor(dataset), Time_Sec=median_time, Line_Type = as.factor(line_type))
ress1 <- melt(ress1, id.vars='Dataset')
save(ress1, file="size.Rdata")

print(g <- ggplot(ress1, aes(Dataset, value)) + geom_bar(aes(fill = variable), position = "dodge", stat="identity")+ leg + labs(title="Forest Size", x="Dataset", y="Average Tree Size (Mb)", subtitle=paste("")))
#print(ggplot(ress2,aes(x=Cores_Used, y=Scale_Up, group=Line_Type, color=Line_Type))+geom_line()+labs(title="R-RerF Scale-Up", x="Number of Cores", y="Scale-Up", subtitle=paste("Initial number of samples: ", baseS))+expand_limits(y=c(0,1))+leg)
```
