---
title: "Test speed-up and scale-up of R-Rerf against xg and ranger"
author: "James Browne"
date: "Oct 10 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = FALSE)
##source('rfr_function.R')
library(ggplot2)
nTimes <- 10
run_su <- TRUE
leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))


```{r speed_up_printRerf, cache = FALSE}
if(FALSE){
load(file="exp0027speedUpRerf.Rdata")
ressTemp <- ress1
load(file="exp0027speedUpXG.Rdata")
ressTemp <- rbind(ressTemp[1:4,], ress1)
Line_Type <- c("RerF", "RerF", "RerF", "RerF", "XGBoost", "XGBoost", "XGBoost", "XGBoost", "Ideal", "Ideal", "Ideal", "Ideal")
ressTemp <- cbind(Line_Type, ressTemp[,2:4])
lab <- labs(title="Forest Algorithm Strong Scaling", x="Number of Cores", y="Relative Performance", subtitle =paste("Dataset Size: 168MB"))
print(ggplot(ressTemp,aes(x=Cores_Used, y=Speed_Up, group=Line_Type, color=Line_Type))+geom_line()+lab +leg +scale_y_continuous(trans = "log2", breaks = c(2,4,8,16)))
gc()
}
```
```{r speed_up_printSXG, cache = FALSE}
if(TRUE){
load(file="exp0027SXG.Rdata")
lab <- labs(title="Forest Algorithm Strong Scaling", x="Number of Cores", y="Relative Performance", subtitle =paste("Dataset Size: MNIST(168MB)"))
print(ggplot(ress1,aes(x=Cores_Used, y=Speed_Up, group=Line_Type, color=Line_Type))+geom_line()+lab +leg +scale_y_continuous(trans = "log2", breaks = c(2,4,8,16,32)))
gc()
}
```

