---
title: "Print the results of exp0002run4"
author: "James Browne"
date: "June 30 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = FALSE)
source('rfr_function.R')
library(ggplot2)
leg <- theme(legend.text = element_text(size = 12), legend.title=element_blank(), plot.title = element_text(size = 16,  face="bold"), plot.subtitle = element_text(size = 12),axis.title.x = element_text(size=12), axis.text.x = element_text(size=12), axis.title.y = element_text(size=12), axis.text.y = element_text(size=12))
run_mnist <-TRUE 
run_random <-TRUE#TRUE 
run_higgs <-TRUE #FALSE
baseS <- 2500
```

**********************************************************************
#### Scale-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Scale Up, proportional increase in resource (number of samples and cores).  
**********************************************************************

```{r scale-up-n_print, cache = FALSE}
if(run_mnist){
load(file="exp0002scaleUpMnist.Rdata")
Tics <- scale_y_continuous(breaks=c(0.0,0.5,1.0),labels=c(0.0,0.5,1.0))
print(ggplot(ress2,aes(x=Cores_Used, y=Scale_Up, group=Line_Type, color=Line_Type))+geom_line()+labs(title="R-RerF Weak Scaling (MNIST)", x="Number of Cores", y="Relative Performance", subtitle=paste("MNIST, initial number of samples: ", baseS,"\nIdeal assumes average case complexity\n10 classes, 784 features"))+expand_limits(y=c(0,1))+leg+Tics)
}
```

**********************************************************************
#### Scale-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Scale Up, proportional increase in resource (number of samples and cores).  
**********************************************************************
```{r scale-up-n_print2, cache = FALSE}
if(run_higgs){
load(file="exp0002scaleUpHiggs.Rdata")
Tics <- scale_y_continuous(breaks=c(0.0,0.5,1.0),labels=c(0.0,0.5,1.0))
print(ggplot(ress1,aes(x=Cores_Used, y=Scale_Up, group=Line_Type, color=Line_Type))+geom_line()+labs(title="R-RerF Weak Scaling (HIGGS)", x="Number of Cores", y="Relative Performance", subtitle=paste("Higgs, initial number of samples: ", baseS,"\nIdeal assumes average case complexity\n2 Classes, 31 features"))+expand_limits(y=c(0,1))+leg+Tics)
}
```

**********************************************************************
#### Scale-up, 10 runs impossible data set, MinParent=6, trees=128, MaxDepth=0, bagging = .20, FUN=makeA, options=ncol(X), Breadth First
Scale Up, proportional increase in resource (number of samples and cores).  
**********************************************************************
```{r scale-up-n_print3, cache = FALSE}
if(run_random){
load(file="exp0002scaleUpRandom.Rdata")
Tics <- scale_y_continuous(breaks=c(0.0,0.5,1.0),labels=c(0.0,0.5,1.0))
print(ggplot(ress1,aes(x=Cores_Used, y=Scale_Up, group=Line_Type, color=Line_Type))+geom_line()+labs(title="R-RerF Weak Scaling (Random)", x="Number of Cores", y="Relative Performance", subtitle=paste("Random, initial number of samples: ", baseS,"\nIdeal assumes average case complexity\n10 Classes, 784 features"))+expand_limits(y=c(0,1))+leg+Tics)
}
```
